How accurate are EOM-CC4 vertical excitation energies?

### 2021-05-04 Manuscript/CC4.tex
Corrections Denis

\title{How accurate is CC4 for vertical excitation energies?}

@@

% Abstract
\begin{abstract}
We report the first investigation of the performance of CC4 --- an approximate coupled-cluster model which includes iteratively quadruple excitations --- for vertical excitation energies in molecular systems.
By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy in very close agreement with its more expensive CCSDTQ parent.
Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states.
\end{abstract}

@@

Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods which delivers increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \le n$ and $n$ is the number of electrons). \cite{Cizek_1966,Paldus_1972,Crawford_2000,Bartlett_2007,Shavitt_2009}
Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system for a given basis set.
However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods  (\ie, $k \ll n$) for computational convenience.
Popular choices are CC with singles and doubles (CCSD), \cite{Cizek_1966,Purvis_1982} CC with singles, doubles, and triples (CCSDT), \cite{Noga_1987a,Scuseria_1988} CC with singles, doubles, triples, and quadruples (CCSDTQ), \cite{Oliphant_1991,Kucharski_1992} and 
CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) \cite{Hirata_2000,Kallay_2001} with corresponding computational scalings of $\order*{N^{6}}$, $\order*{N^{8}}$,  $\order*{N^{10}}$, and  $\order*{N^{12}}$, respectively (where $N$ denotes the number of orbitals).
An alternative, systematically-improvable family of methods is defined by the CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b,Koch_1997} and CC4 \cite{Kallay_2005} series of models which have been introduced by the Aarhus group in the context of CC response theory. \cite{Christiansen_1998}
These iterative methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
A somehow similar strategy has been applied to produce the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
Of course, a plethora of approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details. \cite{Crawford_2000,Piecuch_2002,Bartlett_2007,Shavitt_2009}

Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate equilibrium geometries, \cite{Kallay_2003} potential energy surfaces, vibrational frequencies, \cite{Kallay_2004a} Born-Oppenheimer corrections, \cite{Gauss_2006} and a vast panel of properties such as dipoles (and higher moments), \cite{Kallay_2003}  NMR chemical shifts, \cite{Kallay_2004a} magnetizabilities, \cite{Gauss_2009} polarizabilities, \cite{Kallay_2006} etc.
Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states \cite{Monkhorst_1977} thanks to the equation-of-motion (EOM) \cite{Emrich_1981,Comeau_1993,Stanton_1993,Krylov_2008} and linear-response (LR) \cite{Ghosh_1981,Sekino_1984,Koch_1990a,Koch_1990b,Rico_1993} formalisms which are known to produce identical excitation energies but different properties. \cite{Chrayteh_2021,Sarkar_2021}
In EOM-CC, one determines vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
A more general procedure to compute excitation energies that can be applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate excitation energies with the ``complete'' series CCSD, \cite{Stanton_1993} CCSDT, \cite{Kowalski_2001,Kucharski_2001} CCSDTQ, \cite{Hirata_2004} CCSDTQP, \cite{Kallay_2004b} \ldots~or the ``approximate'' series CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b} CC4, \cite{Kallay_2004b} \ldots~while retaining the formal scaling of their ground-state analog.

Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} has (re)appeared \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018,Eriksen_2019} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically important determinants thanks to a suitable criterion usually based on perturbation theory. \cite{Huron_1973,Garniron_2017,Sharma_2017,qp2}
By iteratively increasing the number of determinants of the variational space and supplemented it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.\cite{Holmes_2017,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,qp2,Veril_2021}
Although the formal scaling of such algorithms remain exponential, the prefactor is greatly reduced which explains their current attractiveness in the electronic structure community and much wider applicability than their common FCI parent.

Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset gathering more than 500 highly-accurate vertical excitation energies for electronic transitions of various natures (valence, Rydberg, $\npis$, $\pipis$, singlet, doublet, triplet, charge-transfer, and double excitations) in small- and medium-sized molecules ranging from diatomics to molecules as large as naphthalene. \cite{Loos_2018a,Loos_2019,Loos_2020a,Loos_2020b,Loos_2020c,Veril_2021}
The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable comparisons between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
Most of these reference transition energies, which rely exclusively on high-level \textit{ab initio} calculations, can be reasonably considered as chemically accurate, \ie, within \SI{1}{\kcal\per\mol} or \SI{0.043}{\eV} of the FCI limit.
However, their accuracy may rapidly deteriorate, in particular, as the system size grows.
Indeed, it is usually challenging to compute reliable SCI+PT2 estimates or CCSDTQ excitation energies for molecules with more than four non-hydrogen atoms.
Therefore, for the larger molecules of the QUEST database, we mostly relied on CCSDT to define reference excitation energies.
Of course, it would be highly valuable to have access to more accurate methods (including, at least, quadruple excitations) in order to refine, in the near future, these theoretical best estimates.

In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the most expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer, \ldots) and spatial symmetries obtained with various high-level CC methods.
Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} to the best of our knowledge, CC4 has never been considered to compute excited-states energies before.
As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.

@@

All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the system considered here have been extracted from previous studies at the exception of \ce{BH} and \ce{BF}. \cite{Loos_2018a}
In the following, we consider diffuse-containing Dunning's double- and triple-$\zeta$ basis sets (aug-cc-pVDZ and aug-cc-pVTZ).
Note that CCSDTQP energies could only be computed for the smaller basis (aug-cc-pVDZ).

@@

Table \ref{tab:BigTab} gathers, for the two considered basis sets, the 25 vertical excitation energies computed for our set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are also reported for these models for the aug-cc-pVDZ basis.
These statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
Note, in particular, the significant improvement brought by CC4 in terms of MAE and MSE as compared to the third-order methods, CC3 and CCSDT, which shows how important can be quadruple excitations when one aims for high accuracy.
The distribution of the errors are reported in Fig.~\ref{fig:error} for each level of theory.
The FCI estimates shows how accurate are the CCSDTQP reference data with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis.
For the larger aug-cc-pVTZ basis, the CCSDTQ and FCI remain in excellent agreement although the error bars associated with the extrapolated FCI values prevent us from any quantitative comparisons.

For the two basis sets, the key result that we would like to highlight here is the outstanding similarity of the CC4 and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with the aug-cc-pVDZ (aug-cc-pVTZ) basis set.
Overall, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) with only a rather minor improvement going from CC4 to CCSDTQ.

@@

We can therefore conclude that, for this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a significant improvement of its third-order version, CC3, and the ``complete'' CCSDT method.
Although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$].
This will certainly allow us to revisit, in the near future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
This work was performed using HPC resources from CALMIP (Toulouse) under allocation 2021-18005.
PFL has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
DJ is indebted to the CCIPL computational center installed in Nantes for (the always very) generous allocation of computational time. 
He also thanks the ANR for financial support in the framework of the BSE-forces grant (ANR-20-CE29-0005).
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\title{How accurate are EOM-CC4 vertical excitation energies?}

@@

% Abstract
\begin{abstract}
We report the first investigation of the performance of EOM-CC4 --- an approximate equation-of-motion coupled-cluster model which includes iteratively quadruple excitations --- for vertical excitation energies in molecular systems.
By considering a set of 25 excited states in 8 small molecules for which we have computed CCSDTQP and FCI reference energies, we show that CC4 yields excitation energies with sub-kJ~mol$^{-1}$ accuracy, in very close agreement with its more expensive CCSDTQ parent.
Therefore, if one aims at high accuracy, CC4 stands as a highly competitive approximate method to model molecular excited states, significantly improving over both CC3 and CCSDT.
\end{abstract}

@@

Single-reference coupled-cluster (CC) theory provides a hierarchy of size-extensive methods delivering increasingly accurate energies and properties via the systematic increase of the maximum excitation degree of the cluster operator $\hT = \hT_1 + \hT_2 + \ldots + \hT_k$ (where $k \le n$ and $n$ is the number of electrons). \cite{Cizek_1966,Paldus_1972,Crawford_2000,Bartlett_2007,Shavitt_2009}
Without any truncation (\ie, $k = n$), the so-called full CC (FCC) method is equivalent to full configuration interaction (FCI), hence providing the exact energy and wave function of the system for a given atomic basis set.
However, it is not computationally viable due to its exponential scaling with system size, and one has to resort to truncated CC methods  (\ie, $k \ll n$) for computational convenience.
Popular choices are CC with singles and doubles (CCSD), \cite{Cizek_1966,Purvis_1982} CC with singles, doubles, and triples (CCSDT), \cite{Noga_1987a,Scuseria_1988} CC with singles, doubles, triples, and quadruples (CCSDTQ), \cite{Oliphant_1991,Kucharski_1992} and 
CC with singles, doubles, triples, quadruples, and pentuples (CCSDTQP) \cite{Hirata_2000,Kallay_2001} with corresponding computational scalings of $\order*{N^{6}}$, $\order*{N^{8}}$,  $\order*{N^{10}}$, and  $\order*{N^{12}}$, respectively (where $N$ denotes the number of orbitals).
An alternative, systematically-improvable family of methods is defined by the CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b,Koch_1997} and CC4 \cite{Kallay_2005} series of models which have been introduced by the Aarhus group in the context of CC response theory. \cite{Christiansen_1998}
These iterative methods scale as $\order*{N^{5}}$, $\order*{N^{7}}$, and $\order*{N^{9}}$, respectively, and can be seen as cheaper approximations of CCSD, CCSDT, and CCSDTQ, by skipping the most expensive terms and avoiding the storage of the higher-excitation amplitudes.
A somehow similar strategy has been applied to define the CCSDT-3 \cite{Urban_1985,Noga_1987b} and CCSDTQ-3 \cite{Kallay_2005} models based on arguments stemming from perturbation theory.
Of course, a plethora of other approximate CC models have been developed over the years and we refer the interested reader to specialized reviews for more details. \cite{Crawford_2000,Piecuch_2002,Bartlett_2007,Shavitt_2009}

Coupled-cluster methods have been particularly successful for small- and medium-sized molecules in the field of thermodynamics, kinetics, and spectroscopy, thanks to the computations of accurate equilibrium geometries, \cite{Kallay_2003} potential energy surfaces, vibrational frequencies, \cite{Kallay_2004a} Born-Oppenheimer corrections, \cite{Gauss_2006} and a vast panel of properties such as dipoles (and higher moments), \cite{Kallay_2003}  NMR chemical shifts, \cite{Kallay_2004a} magnetizabilities, \cite{Gauss_2009} polarizabilities, \cite{Kallay_2006} etc.
Although originally developed for ground-state energies and properties, CC has been successfully extended to excited states \cite{Monkhorst_1977} thanks to the equation-of-motion (EOM) \cite{Emrich_1981,Comeau_1993,Stanton_1993,Krylov_2008} and linear-response (LR) \cite{Ghosh_1981,Sekino_1984,Koch_1990a,Koch_1990b,Rico_1993} formalisms which are known to produce identical excitation energies but different properties. \cite{Chrayteh_2021,Sarkar_2021}%DJ: Pas sur que les deux meilleures refs ici, si ? Tu veux pas des trucs plus seminaux ?
In EOM-CC, one determines vertical excitation energies via the diagonalization of the similarity-transformed Hamiltonian $\bH = e^{-\hT} \hH e^{\hT}$.
A more general procedure to compute excitation energies that can be applied to any approximate CC model (as the ones mentioned above) consists in diagonalizing the so-called CC Jacobian obtained via the differentiation of the CC amplitude equations.
Again, by systematically increasing the maximum excitation degree of $\hT$, one can systematically produce increasingly accurate EOM/LR excitation energies with the ``complete'' series CCSD, \cite{Stanton_1993} CCSDT, \cite{Kowalski_2001,Kucharski_2001} CCSDTQ, \cite{Hirata_2004} CCSDTQP\cite{Kallay_2004b} \ldots~or the ``approximate'' series CC2, \cite{Christiansen_1995a} CC3, \cite{Christiansen_1995b} CC4 \cite{Kallay_2004b} \ldots~while retaining the formal scaling of their ground-state analog. We drop the EOM prefix below as all our calculations are made within that approach.

Recently, a large collection of deterministic, stochastic or hybrid selected CI (SCI) methods \cite{Bender_1969,Whitten_1969,Huron_1973} made their comeback \cite{Booth_2009,Deustua_2017,Holmes_2016,Eriksen_2017,Xu_2018,Giner_2013,Giner_2015,Evangelista_2014,Tubman_2016,Liu_2016,Ohtsuka_2017,Zimmerman_2017,Coe_2018,Garniron_2018,Eriksen_2019} in the electronic structure landscape providing an alternative route to highly-accurate ground- and excited-state energies \cite{Holmes_2017,Li_2018,Li_2020,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,Loos_2020e,qp2,Eriksen_2020,Yao_2020,Veril_2021} (see Refs.~\onlinecite{Loos_2020a,Eriksen_2021} for recent reviews).
The general idea behind SCI methods is simple: rather than exploring the entire FCI space by systematically increasing the maximum excitation degree of the determinants taken into account (leading to the slowly convergent and size-inconsistent series of methods CISD, CISDT, CISDTQ, \ldots), one performs a sparse exploration of the FCI space by selecting only the most energetically important determinants thanks to a suitable criterion usually based on perturbation theory. \cite{Huron_1973,Garniron_2017,Sharma_2017,qp2}
By iteratively increasing the number of determinants of the variational space and supplementing it with a second-order perturbative correction (PT2), the SCI+PT2 family of methods has been recently shown to produce near-FCI correlation and excitation energies for small- and medium-size molecules in compact basis sets.\cite{Holmes_2017,Loos_2018a,Chien_2018,Loos_2019,Loos_2020b,Loos_2020c,qp2,Veril_2021}
Although the formal scaling of such algorithms remain exponential, the prefactor is greatly reduced which explains their current attractiveness in the electronic structure community and much wider applicability than their standard FCI parent.

Taking advantage of the high accuracy of CC and SCI+PT2 methods, we have very recently created a large dataset gathering more than 500 highly-accurate vertical excitation energies for electronic transitions of various natures (valence, Rydberg, $\npis$, $\pipis$, singlet, doublet, triplet, charge-transfer, and double excitations) in small- and medium-sized molecules ranging from diatomics to molecules as large as naphthalene. \cite{Loos_2018a,Loos_2019,Loos_2020a,Loos_2020b,Loos_2020c,Veril_2021}
The main purpose of this so-called QUEST database is to provide reference excitation energies in order to perform fair and reliable benchmarks between electronic structure methods and assess their strengths and weakness in a large panel of chemical scenarios.
Most of these reference transition energies, which rely exclusively on high-level \textit{ab initio} calculations, can be reasonably considered as chemically accurate, \ie, within \SI{1}{\kcal\per\mol} or \SI{0.043}{\eV} of the FCI limit.
However, their accuracy may rapidly deteriorate, in particular, as the system size grows.
Indeed, it is usually challenging to compute reliable SCI+PT2 estimates or CCSDTQ excitation energies for molecules with more than four non-hydrogen atoms.
Therefore, for the larger molecules of the QUEST database, we mostly relied on CCSDT to define reference excitation energies.
Of course, it would be highly valuable to have access to more accurate methods (including, at least, quadruple excitations) in order to refine these theoretical best estimates.

In this context, the main purpose of the present study is to assess the relative accuracy of the approximate iterative CC4 model against the more expensive CCSDTQ and CCSDTQP methods in the case of vertical excitation energies, as well as its absolute accuracy with respect to FCI.
To do so, we consider a set of 8 small molecules (\ce{NH3}, \ce{BH}, \ce{BF}, \ce{CO}, \ce{N2}, \ce{HCl}, \ce{H2S}, and \ce{H2O}) and we compare the excitation energies associated with 25 singlet excited states of various natures ($\npis$, $\pipis$, Rydberg, valence, charge-transfer\ldots) and spatial symmetries obtained with various high-level CC methods.
Although a small number of studies have been published on the performance of CC4 for ground-state energies and properties, \cite{Kallay_2005,Matthews_2015a,Matthews_2021} this work stands, to the best of our knowledge, as the first to consider CC4  to compute excited-states energies.
As we shall see below, CC4 is an excellent approximation to its CCSDTQ parent, and produces excitation energies with sub-\si{\kJ\per\mol} accuracy for this set of small molecules, well below the chemical accuracy threshold.

@@

All calculations have been performed in the frozen-core approximation and the CC3/aug-cc-pVTZ geometries of the system considered here have been extracted from previous studies. \cite{Loos_2018a,Chrayteh_2021}
In the following, we consider diffuse-containing Dunning's double- and triple-$\zeta$ basis sets (aug-cc-pVDZ and aug-cc-pVTZ).
Note that CCSDTQP energies could only be computed for the smaller basis (aug-cc-pVDZ).

@@

Table \ref{tab:BigTab} gathers, for the two considered basis sets, the 25 vertical excitation energies computed for our set of 8 molecules with various CC models as well as the FCI estimates computed with CIPSI.
First, we underline that the FCI estimates show how accurate are the CCSDTQP reference data are, with a maximum deviation of \SI{0.002}{\eV} when one considers the aug-cc-pVDZ basis. For the larger aug-cc-pVTZ basis, 
the CCSDTQ and FCI remain in excellent agreement although the error bars associated with the extrapolated FCI values prevent us from any quantitative comparisons.

The mean absolute errors (MAEs) and mean signed errors (MSEs) with respect to CCSDTQP are reported in the bottom of  Table \ref{tab:BigTab} for the CC2-to-CCSDTQ models for the aug-cc-pVDZ basis.
The distribution of the errors are reported in Fig.~\ref{fig:error} for each level of theory.
The statistical quantities nicely illustrate the systematic improvement of the transition energies when one ramps up the computational effort following the series CC2, CCSD, CC3, CCSDT, CC4, and CCSDTQ.
We note that the errors decrease by ca. one order of magnitude when switching from CCSD to CC3 and from CCSDT to CC4, whilst improvements of ca. 50\%\ ``only'' are noted when going from
approximate to full levels, i.e., when going from CC2 to CCSD, from CC3 to CCSDT, and from CC4 to CCSDTQ. In other works  CC4 brings significant improvement in terms of MAE and MSE as compared to 
the third-order methods, CC3 and CCSDT, which demonstrates the importance of quadruple excitations when one aims for high accuracy.  Besides, for the two basis sets, there is an outstanding similarity of the CC4 
and CCSDTQ excitation energies with mean absolute and signed deviations below (equal to) \SI{0.001}{\eV} and a maximum deviation of \SI{0.011}{\eV} (\SI{0.007}{\eV}) between to the two sets of data obtained with 
the aug-cc-pVDZ (aug-cc-pVTZ) basis set. Therefore, including quadruples allows to reach sub-\si{\kJ\per\mol} accuracy (\ie, average error below \SI{0.01}{\eV}) with only a rather minor improvement going from CC4 to CCSDTQ.

@@

For this set of small molecules at least, CC4 is a rather competitive approximation to its more expensive CCSDTQ parent as well as a very significant improvement of its third-order version, CC3, and the ``complete'' CCSDT method.
This finding is promising, though we are well aware that the conclusions obtained for small and larger molecules might differ, i.e., CCSD outperforms CC2 for compact molecules (as here), but the reverse trend is often found
for larger compounds.\cite{Loos_2018a,Loos_2020a,Veril_2021} Therefore, although further investigations on larger compounds are definitely required, the present results are very encouraging as CC4, with its $\order*{N^9}$ scaling, 
can be applied to significantly larger molecules than CCSDTQ [which scales as $\order*{N^{10}}$]. This will likely allow us to revisit, in the future, some of the theoretical best estimates defined in the context of the QUEST database.\cite{Loos_2020a,Veril_2021}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
PFL has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481).
This work was performed using HPC resources from CALMIP (Toulouse) under allocation 2021-18005 and of the CCIPL computational center installed in Nantes.
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
